---
title: A spatial database of $CO_2$ emissions and urban form fragmentation for the
  low carbon urban system in Jinjiang city, China
author: "[Shaoqing Dai](http://gisersqdai.top/mycv/), Shudi Zuo, Yin Ren"
csl: ehp.csl
output:
  html_document:
    df_print: paged
    toc: yes
    toc_float:
      collapsed: true
      smooth_scroll: true
bibliography: CEMU.bib
---



# Brief

A spatial database of low carbon urban system represented the spatial distribution maps of $CO_2$ emissions, urban form metrics (urban landscape fragmentation), proportion of urban area (PUA) and points of interest density (POID) at two resolutions: 30 m ($R_{30m}$) and 500 m ($R_{500m}$) in Jinjiang city, China. The data were produced by ArcGIS 10.2, Apack 2.23, Fragstats 4.2 and R 3.5.3. All the data were stored in Geotiff format.

The names of corresponding data were given in the [ReadMe.txt](http://science.gisersqdai.top/DIB/DataDescription.txt).

The data published in [Data in Brief](https://doi.org/10.1016/j.dib.2020.105274).

[Github](https://github.com/GISerDaiShaoqing/Urban-Carbon-Dioxide-sources-gridded-maps-and-its-detemination-in-Jinjiang-city)

# Open datasets

## Total emission estimation
"Total", "Resident", "Industry" and "Transport" represent the total-, resident-, industrial-, and transport- $CO_2$ emissions in Jinjiang City respectively. 
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(plotly)
cepopalluseghg <- 2596088.162
ceindustryalluseghg <- 13729257.32
cetransalluseghg <- 298076.991

datace <- data.frame(sector = c("Residential", "Industry", "Transport"), emission = c(2596088.162, 13729257.32,
                                                                                      298076.991))

p <- plot_ly(datace, labels = ~sector, values = ~emission, type = 'pie')%>%
   layout(title = 'Emissions from different sectors in 2013',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
p
```

## Spatial distribution maps of $CO_2$ emissions
### 30 m resolution maps
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(raster)
library(leafsync)
library(mapview)

COP30 <-  raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/Uncertainty/Mapping/COP30.tif")
COI30 <- raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/Uncertainty/Mapping/COI30.tif")
COT30 <- raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/Uncertainty/Mapping/COT30.tif")
CO30 <- raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/Uncertainty/Mapping/CO30.tif")

m1 <- mapview(CO30, layer.name = "Total (t)")
m2 <- mapview(COP30, layer.name = "Resident (t)")
m3 <- mapview(COI30, layer.name = "Industry (t)")
m4 <- mapview(COT30, layer.name = "Transport (t)")
sync(m1, m2, m3, m4)
```

Download links as follow:

"Total", "Resident", "Industry" and "Transport" represent the total, resident, industrial, and Transport $CO_2$ emissions in Jinjiang City respectively. 

[Total](http://science.gisersqdai.top/DIB/CO30.tif)

[Resident](http://science.gisersqdai.top/DIB/COR30.tif)

[Industry](http://science.gisersqdai.top/DIB/COI30.tif)

[Transport](http://science.gisersqdai.top/DIB/COT30.tif)


### 500 m resolution maps
```{r echo=FALSE, message=FALSE, warning=FALSE}
COP500 <-  raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/Uncertainty/Mapping/COP500.tif")
COI500 <- raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/Uncertainty/Mapping/COI500.tif")
COT500 <- raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/Uncertainty/Mapping/COT500.tif")
CO500 <- raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/Uncertainty/Mapping/CO500.tif")

m5 <- mapview(CO500, layer.name = "Total (t)")
m6 <- mapview(COP500, layer.name = "Resident (t)")
m7 <- mapview(COI500, layer.name = "Industry (t)")
m8 <- mapview(COT500, layer.name = "Transport (t)")

sync(m5, m6, m7, m8)
```

Download links as follow:

"Total", "Resident", "Industry" and "Transport" represent the total, resident, industrial, and Transport $CO_2$ emissions in Jinjiang City respectively. 

[Total](http://science.gisersqdai.top/DIB/CO500.tif)

[Resident](http://science.gisersqdai.top/DIB/COR500.tif)

[Industry](http://science.gisersqdai.top/DIB/COI500.tif)

[Transport](http://science.gisersqdai.top/DIB/COT500.tif)

## The mixing degree of urban functional district (UFD)

```{r echo=FALSE, message=FALSE, warning=FALSE}
fcmix30 <-  raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/mixed/planningfunctionmix.tif")
fcmix500 <- raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/mixed/functionmix500m.tif")

m9 <- mapview(fcmix30*100, layer.name = "R 30 m (%)")
m10 <- mapview(fcmix500*100, layer.name = "R 500 m (%)")

sync(m9, m10)
```

Download links as follow:

[R 30 m](http://science.gisersqdai.top/DIB/fcmix30.tif)
[R 500 m](http://science.gisersqdai.top/DIB/fcmix500.tif)

## Lacunarity indices
We used Apack 2.23 calculated the Lacunarity indicies. 

```{r echo=FALSE, fig.height=5, fig.width=8, message=FALSE, warning=FALSE, paged.print=FALSE}
library(ggplot2)
library(ggthemr)
library(gridExtra)

windowsFonts(RT = windowsFont("Times New Roman"))

LCU<-read.table("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/Scale/LCU.txt",sep="")
lftype1<-c("Land use patches","Functional district patches")
lftype1<-rep(lftype1,each=300)
LCU30<-data.frame(size=LCU$V4[c(1:600)],lacunarity=LCU$V6[c(1:600)],type=lftype1)

lftype2<-c("Land use patches","Functional district patches")
lftype2<-rep(lftype2,each=20)
LCU500<-data.frame(size=LCU$V4[c(601:640)],lacunarity=LCU$V6[c(601:640)],type=lftype2)

ggthemr("fresh")

LCUplot<-rbind(LCU30,LCU500)

cpx1<-2.489
cpy1<--0.2597244*cpx1+0.0611177*cpx1^2-0.0081856*cpx1^3+1.1797186
cpx2<-3.080
cpy2<--0.4223577*cpx2+0.0943508*cpx2^2-0.0102114*cpx2^3+1.4059355
cpx3<-log(LCUplot[602,1])
cpy3<-log(LCUplot[602,2])
cpx4<-log(LCUplot[622,1])
cpy4<-log(LCUplot[622,2])
cpx1<-rep(cpx1,300)
cpx2<-rep(cpx2,300)
cpx3<-rep(cpx3,20)
cpx4<-rep(cpx4,20)
cpx<-c(cpx1,cpx2,cpx3,cpx4)
cpy<-c(cpy1,cpy2,cpy3,cpy4)
cptype<-c("Land use patches","Functional district patches")
cptype<-rep(cptype,2)
cpscale<-c("(a)","(b)")
cpscale<-rep(cpscale,2)
cpxy<-data.frame(cpx,cpy)
cpxline<-data.frame(cpx,type=cptype,scale=cpscale)

LCUplot<-rbind(LCU30,LCU500)
scaleLCU<-c("(a)","(b)")
scaleLCU<-rep(scaleLCU,each=600)
scaleLCU<-scaleLCU[1:640]
LCUplot<-data.frame(LCUplot,scale=scaleLCU)
LCUplot<-data.frame(LCUplot,scale=scaleLCU,cpxy)

p30<-ggplot(subset(LCU30, LCU30$type=="Functional district patches"))+geom_point(mapping=aes(x=log(size),y=log(lacunarity),colour=type,shape=type))+
  geom_line(mapping=aes(x=log(size),y=log(lacunarity),colour=type))+
  geom_vline(xintercept=cpx[1:2],color="red",linetype="dashed")+
  ylim(0,1.5)+labs(x="ln(box size)/cell",y="ln(Lacunarity)",title="(a)")+
  theme(legend.position="None",title=element_text(size=25,family="RT"),axis.text.y=element_text(size=25,family="RT"),
        axis.text.x=element_text(size=25,family="RT"),axis.title=element_text(size=25,family="RT"),
        strip.text=element_text(size=25,family="RT"))

p500<-ggplot(subset(LCU500, LCU500$type=="Functional district patches"))+geom_point(mapping=aes(x=log(size),y=log(lacunarity),colour=type,shape=type))+
  geom_line(mapping=aes(x=log(size),y=log(lacunarity),colour=type))+
  geom_vline(xintercept=cpx[3:4],color="red",linetype="dashed")+
  ylim(0,0.75)+labs(x="ln(box size)/cell",y="ln(Lacunarity)",title="(b)")+
  theme(legend.position="Null",legend.title=element_text(size=25,family="RT"),
        legend.text=element_text(size=25,family="RT"),legend.key.height=unit(1,"cm"),
        title=element_text(size=25,family="RT"),axis.text.y=element_text(size=25,family="RT"),
        axis.text.x=element_text(size=25,family="RT"),axis.title=element_text(size=25,family="RT"),
        strip.text=element_text(size=25,family="RT"))
scaleplot<-grid.arrange(p30,p500,nrow=1)
```


Download links as follow:

[R 30 m](http://science.gisersqdai.top/DIB/LCU30.txt)
[R 500 m](http://science.gisersqdai.top/DIB/LCU500.txt)

## Landscape metrics
Fragstats 4.2 software was used to calculate the number of patches (NP), patch density (PD), division (DIVISION) and effective mesh size (MESH) metrics.

### 30 m resolution maps
```{r echo=FALSE, message=FALSE, warning=FALSE}
NP30 <-  raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/EcologicalIndex/multiplelandscape/planningfunction30/np.tif")
PD30 <- raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/EcologicalIndex/multiplelandscape/planningfunction30/pd.tif")
DIVISION30 <- raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/EcologicalIndex/multiplelandscape/planningfunction30/division.tif")
MESH30 <- raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/EcologicalIndex/multiplelandscape/planningfunction30/mesh.tif")

m11 <- mapview(NP30, layer.name = "NP")
m12 <- mapview(PD30, layer.name = "PD")
m13 <- mapview(DIVISION30, layer.name = "DIVISION")
m14 <- mapview(MESH30, layer.name = "MESH")
sync(m11, m12, m13, m14)
```

Download links as follow:

[NP](http://science.gisersqdai.top/DIB/np30.tif)

[PD](http://science.gisersqdai.top/DIB/pd30.tif)

[DIVISION](http://science.gisersqdai.top/DIB/division30.tif)

[MESH](http://science.gisersqdai.top/DIB/mesh30.tif)

### 500 m resolution maps
```{r echo=FALSE, message=FALSE, warning=FALSE}
NP500 <-  raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/EcologicalIndex/multiplelandscape/function500/np.tif")
PD500 <- raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/EcologicalIndex/multiplelandscape/function500/pd.tif")
DIVISION500 <- raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/EcologicalIndex/multiplelandscape/function500/division.tif")
MESH500 <- raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/EcologicalIndex/multiplelandscape/function500/mesh.tif")

m15 <- mapview(NP500, layer.name = "NP")
m16 <- mapview(PD500, layer.name = "PD")
m17 <- mapview(DIVISION500, layer.name = "DIVISION")
m18 <- mapview(MESH500, layer.name = "MESH")
sync(m15, m16, m17, m18)
```

Download links as follow:

[NP](http://science.gisersqdai.top/DIB/np500.tif)

[PD](http://science.gisersqdai.top/DIB/pd500.tif)

[DIVISION](http://science.gisersqdai.top/DIB/division500.tif)

[MESH](http://science.gisersqdai.top/DIB/mesh500.tif)

## Impact factors of the $CO_2$ mitigation: PUA and POID

### PUA

```{r echo=FALSE, message=FALSE, warning=FALSE}
PUA30 <- raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/Interaction/UrbanArea/PUA30.tif")
PUA500 <- raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/Interaction/UrbanArea/PUA500.tif")

m19 <- mapview(PUA30*100, layer.name = "R 30 m (%)")
m20 <- mapview(PUA500*100, layer.name = "R 500 m (%)")

sync(m19, m20)
```

Download links as follow:

[R 30 m](http://science.gisersqdai.top/DIB/PUA30.tif)

[R 500 m](http://science.gisersqdai.top/DIB/PUA500.tif)

### POID

```{r echo=FALSE, message=FALSE, warning=FALSE}
POID30 <- raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/datashareuse/POID30.tif")
POID500 <- raster("F:/GISproject/IUE/CarbonEmission/Final/SecondResult/datashareuse/POID500.tif")

m21 <- mapview(POID30, layer.name = "R 30 m")
m22 <- mapview(POID500, layer.name = "R 500 m")

sync(m21, m22)
```


Download links as follow:

[R 30 m](http://science.gisersqdai.top/DIB/POID30.tif)

[R 500 m](http://science.gisersqdai.top/DIB/POID500.tif)

## Uncertainty

We also assessed the uncertainty of Spatial distribution maps of $CO_2$ emissions, detailed information could see the [published paper](https://www.mdpi.com/2072-4292/12/23/3932) and [website](http://science.gisersqdai.top/RSunco2/rsbrief.html).



# Reference 
If you used the data[@rs12233932; @Dai2018sacp; @ZUO2019118659; @DAI2020105274; @shaoqing_dai_2019_3566073], please cited as follow:
